Embodied Neuromorphic Benchmarks

### 2015-08-16 paper/paper.tex
Added horns of dilemma; added ref to NEF

[TODO: maybe add a paragraph summarizing the horns of the dilemma so as to set up the
role of minimal simulation more?]

@@

The above considerations seem to indicate that even though using real-world
physical hardware for benchmarking is problematic, it is still better than
using simplistic simulations which may not generalize to real tasks.  However,
we do not think this is the case.  Instead, we believe neuromorphic benchmarking can effectively exploit an approach 
known as \emph{Minimal Simulation}
(\citealt{Jakobi97evolutionaryrobotics}).

@@

Notice that we can think of this system as a three-layer neural
network, where the input and output layers are linear.  The first layer is $q$, the input state, one value for each joint.  The ``hidden'' layer
is the neurons producing activities $A$, the activity of a large number of neurons.  The output layer again has
one value per joint, and is the extra added signal to apply to the motors, $Ad$.
Given that this is a canonical example of the use of neural networks, we
expect that the majority of neuromorphic hardware is flexible enough to implement
this model.  Importantly, it functions well with spiking neuron models as 
well as non-spiking ones.  For spiking neurons, we consider $A$ to be the
instantaneous measure of the output of a neuron (i.e. whether or not it is currently outputting a spike),
filtered through a low-pass filter.  Further discussion of this sort of learning
rule and comparison to biological spiking neurons can be found in (\citealt{bekolay2013}).

@@

For our specific demonstration, we describe an easy-to-build system that can be usefully controlled
by this adaptive method.  In particular, we use the Lego Mindstorms EV3 robot kit,
organized as shown in [TODO: add figure].  It consists of a single
motor, mounted in such a way that there is a significant amount of weight on
the arm itself (i.e., the weight of the motor itself).  Multiple motors can be
added, and other configurations can be considered and should also be suitable
for testing control, but here we consider only this basic case.

@@

\textit{Funding\textcolon} 
NSERC Discovery (grant 261453),
ONR (N000141310419)
AFOSR (FA8655-13-1-3084),
Canada Research Chairs,
and Canadian Foundation for Innovation
Ontario Innovation Trust.

@@

>>>>

We are thus left with a situation where any benchmark we might define for
a rich, embodied task will be either impractical for different researchers to
run (if it is physically embodied), or inapplicable to real-world situations
(if it is performed in simulation).  Neither option is particularly appealing.

@@

The above considerations could be taken as an argument that even though using real-world
physical hardware for benchmarking is problematic, it is still better than
using simplistic simulations which may not generalize to real tasks.  However,
we do not think this is the case.  Instead, we believe neuromorphic benchmarking can effectively exploit an approach 
known as \emph{Minimal Simulation}
(\citealt{Jakobi97evolutionaryrobotics}).

@@

Notice that we can think of this system as a three-layer neural
network, where the input and output layers are linear.  The first layer is $q$, the input state, one value for each joint.  The ``hidden'' layer
is the neurons producing activities $A$, the activity of a large number of neurons.  The output layer again has
one value per joint, and is the extra added signal to apply to the motors, $Ad$.
Given that this is a canonical example of the use of neural networks, we
expect that the majority of neuromorphic hardware is flexible enough to implement
this model.  Importantly, it functions well with spiking neuron models as 
well as non-spiking ones.  For spiking neurons, we consider $A$ to be the
instantaneous measure of the output of a neuron (i.e. whether or not it is currently outputting a spike),
filtered through a low-pass filter.  Further discussion of this sort of learning
rule and comparison to biological spiking neurons can be found in (\citealt{bekolay2013}).
This type of neural modelling forms the foundation of \cite{eliasmith2003}'s
Neural Engineering Framework, and \cite{stewart2014} have shown that spiking
and non-spiking neurons can be used in this manner to implement a wide
variety of computations.

@@

For our specific demonstration, we describe an easy-to-build system that can be usefully controlled
by this adaptive method.  In particular, we use the Lego Mindstorms EV3 robot kit,
organized as shown in Figure \ref{fig:lego}.  It consists of a single
motor, mounted such that the full weight of a second (unused) motor applies
a significant force on the arm itself.  Multiple motors can be
added, and other configurations can be considered and should also be suitable
for benchmarking, but here we consider only this basic case.

@@

\textit{Funding\textcolon} 
NSERC Discovery (grant 261453),
ONR (N000141310419)
AFOSR (FA8655-13-1-3084),
Mitacs Postdoctoral Fellowship,
Canada Research Chairs,
Canadian Foundation for Innovation,
Ontario Innovation Trust.

@@

\begin{figure}[h!]
\begin{center}
\includegraphics[width=18cm]{figures/lego}
\end{center}
 \textbf{\refstepcounter{figure}\label{fig:lego} Figure \arabic{figure}.}{ A
     simple physical robot embodiment for calibrating the minimal simulation.
     To rotate the central motor to the desired position $q$, enough force
 must be added to $u$ to counteract the weight of the second unused motor.}
\end{figure}
